Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-09-08 ms.tex
removed all \textbf commands since we will have new highlighed changes.

\begin{abstract}
\textbf{L dwarfs} exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations \textbf{yields} insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs \textbf{that have variability reported in the literature}, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a \textbf{nearby reference star}, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no clear spectral dependence, while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m. \textbf{We do not detect} statistically significant phase variations with wavelength. The different variability \textbf{behavior} of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader survey.
\end{abstract}

@@

The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}.
\textbf{These structures} may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}) \textbf{and} long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}). Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}. Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).

Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows \textbf{for} the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity. The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A} \textbf{and} amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) \textbf{and} surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsations. Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact \textbf{with} clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.

Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient \textbf{numbers of nearby reference stars which can be used to correct time-variable telluric absorption} \citep{2003MNRAS.339..477B}.
In contrast, the stability of space-based platforms such as $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision \textbf{and} have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}. However, these facilities are poorly suited for building up robust statistical samples to assess the physical origins of surface heterogeneity \textbf{or} evolution in variability modes.

Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which \textbf{reference stars} are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}). \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby \textbf{reference star} in a wide \textbf{and long (3$\arcsec \times 60 \arcsec$) slit.}
This was sufficient to infer the presence of a cloud/haze layer \textbf{or disfavor TiO/VO absorption} in CoRoT-1b via transmission spectroscopy. A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}. In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion. These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.

@@

\begin{figure*}
\centering
	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
	\label{fig:image1821}
	\vspace{-.9in}
	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right)
	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).  Each image is centered on the target \textbf{and spans} a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left.
	The \textbf{reference stars labeled in each image are observed simultaneously in the 3$\arcsec \times 60 \arcsec$ SpeX slit to remove telluric variability.}}
	\label{fig:images}
	\vspace{0.17in}
\end{figure*}

@@

We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}. The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree}.
\textbf{We downselected} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) \textbf{reference stars} at apparent separations of 5$\arcsec$--30$\arcsec$.
We identified 30 potential targets \textbf{and} prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.  Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).

2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 7.27$\pm$0.02~pc; \citealt{2016AJ....152...24W}) L5 dwarf that shows signatures of \textbf{low surface gravity \citep[][however, see \citet{2015ApJS..219...33G}]{2016ApJ...833...96L}. 
There is no Li I absorption reported for this source \citep{2003AJ....126.2421C,2015ApJS..220...18B}; however its low temperature \citep[T$_{eff}$=1800~K][]{2015ApJS..219...33G} and likely youth ($<$1 Gyr) is consistent with a mass below the hydrogen-burning mass limit \citep{2003A&A...402..701B,2000ApJ...531..438B}.}
This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius\footnote{We adopt the equatorial radius of Jupiter, {\rjup} = 7.15$\times$10$^9$~cm.} R = 1~{\rjup}.
There is an $H$ = 12.3 \textbf{reference star} (2MASS~J08354383$-$0819212) at a separation of 28$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).

2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L} \textbf{and Li absorption \citep{2008ApJ...686..528L}.}
This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}  \citep{2010ApJ...723..684B}, suggesting a near equator-on orientation.  \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
There are three suitably bright \textbf{reference} stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}. We chose 2MASS~J18212622+1414064 \textbf{(visible in Figure~\ref{fig:images})} with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.

To characterize the atmospheric regions probed by our observations, we analyzed previously 
obtained IRTF/SpeX data for these sources \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} \textbf{indicates} near-infrared
classifications of L7 for {\sha} and L5 for {\shb} (Figure~\ref{fig:tbright}). The former is considerably later than the L5 optical classification previously reported by \citet{2003AJ....126.2421C}. We confirm the intermediate low surface gravity classification (INT-G) reported by \citet{2016ApJ...833...96L} based on the indices of \citet{2013ApJ...772...79A} using an L7 classification. The discrepancy between the optical and near-infrared classifications of this source is likely related to surface gravity effects. {\shb}, on the other hand, is a good match to the L5 spectral standard and has a field dwarf gravity classification.

We computed brightness temperature spectra from these data as
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1},
\end{equation}
where the surface flux density $F_{\lambda,surf}$ is computed as
\begin{equation}
F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2.
\end{equation}
$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ \textbf{is} the source distance and $R$ \textbf{is} the source radius.
\textbf{We have ignored limb darkening in our calculations, which affects the surface intensity of brown dwarf surfaces \citep[e.g.][]{2011A&A...529A..75C}.
Since there are few empirical constraints on limb darkening for L-dwarfs, we assume a uniform brightness temperature surface, which gives an average brightness temperature of a non-homogeneous surface.}

Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes. We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming bolometric luminosities from \citet{2015ApJ...810..158F} for {\sha} and from\footnote{The parameters reported for {\shb} in \citet{2016ApJS..225...10F} are in error, but have been updated here based on a forthcoming erratum (J.\ Faherty, 2017, priv.\ comm.).} \citet{2016ApJS..225...10F} for {\shb} (Table~\ref{tab:bdProp}). Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\lbol} and radii were propagated by Monte Carlo simulation.  For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
For {\shb}, we assumed \textbf{a} lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}. The \textbf{\citet{2003A&A...402..701B}} evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.

@@

Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.  The spectral peaks for {\sha} are around 1800--1850~K in the field surface gravity case, and decline from 1700~K at $J$-band (1.2~$\micron$) to 1580~K at $K$-band (2.2~$\micron$) in the low surface gravity case.
We compared these two cases to solar-metallicity BT-Settl spectral models from \citet{2012RSPTA.370.2765A}, with {\teff} and {\logg} parameters consistent with the bolometric luminosity of {\sha} and the adopted ages (again based on the \citealt{2003A&A...402..701B} evolutionary models).
\textbf{To achieve temperatures and gravities between the pre-computed spectra in the BT-Settl atmospheric grid, we interpolated the spectra.}
Both models overlap the data to some degree, although the young model shows an increasing brightness temperature with wavelength rather than a decreasing temperature.  These comparisons slightly favor the field surface gravity case, although differences in the properties of dust between source and models likely play a significant role. For {\shb}, 
brightness temperatures range from 1850~K at $J$-band to 1670~K at $K$-band, again overlapping but declining more strongly with wavelength than the equivalent spectral model, which has a {\teff} similar to that inferred by \citet{2016ApJS..225...10F} and the  \citet{2015ApJ...810..158F} {\teff}/spectral type relation.

\section{Observations}\label{sec:obs}
\begin{deluxetable*}{lcccccccc}[b]
\tablecaption{Observations\label{tab:obsParam}}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{2}{c}{Observation Epoch (UT)} \\
 \cline{2-3}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM \@ $H$} \\
 & &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 272 & 45 & 4.65 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 352 & 60 & 7.47 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including array sampling and overheads. The FWHM is the measured full width \textbf{at} half maximum of the spatial point spread function around \textbf{H band (1.7$\mu$m)}, taken as the median value over the entire time series.}
\end{deluxetable*}

We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. 
Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis. This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes \textbf{differential} color refraction. The effective resolution of the spectral data, set by seeing and pointing errors, \textbf{was} $\lambda$/$\Delta\lambda$ $\approx$ 50. Integration times were 45~s and 60~s for {\sha} and {\shb}, respectively. The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.

>>>>

\begin{abstract}
L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations yields insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs that have variability reported in the literature, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a nearby reference star, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no clear spectral dependence, while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m. We do not detect statistically significant phase variations with wavelength. The different variability behavior of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader survey.
\end{abstract}

@@

The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}.
These structures may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}) and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}). Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}. Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).

Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows for the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity. The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A} and amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsations. Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact with clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.

Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient numbers of nearby reference stars which can be used to correct time-variable telluric absorption \citep{2003MNRAS.339..477B}.
In contrast, the stability of space-based platforms such as $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}. However, these facilities are poorly suited for building up robust statistical samples to assess the physical origins of surface heterogeneity or evolution in variability modes.

Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which reference stars are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}). \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby reference star in a wide and long (3$\arcsec \times 60 \arcsec$) slit.
This was sufficient to infer the presence of a cloud/haze layer or disfavor TiO/VO absorption in CoRoT-1b via transmission spectroscopy. A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}. In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion. These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.

@@

\begin{figure*}
\centering
	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
	\label{fig:image1821}
	\vspace{-.9in}
	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right)
	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).  Each image is centered on the target and spans a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left.
	The reference stars labeled in each image are observed simultaneously in the 3$\arcsec \times 60 \arcsec$ SpeX slit to remove telluric variability.}
	\label{fig:images}
	\vspace{0.17in}
\end{figure*}

@@

We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}. The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree}.
We \textbf{down-selected} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) reference stars at apparent separations of 5$\arcsec$--30$\arcsec$.
We identified 30 potential targets and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.  Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).

2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 7.27$\pm$0.02~pc; \citealt{2016AJ....152...24W}) L5 dwarf that shows signatures of low surface gravity \citep[][however, see \citet{2015ApJS..219...33G}]{2016ApJ...833...96L}. 
There is no Li I absorption reported for this source \citep{2003AJ....126.2421C,2015ApJS..220...18B}; however its low temperature \citep[T$_{eff}$=1800~K][]{2015ApJS..219...33G} and likely youth ($<$1 Gyr) is consistent with a mass below the hydrogen-burning mass limit \citep{2003A&A...402..701B,2000ApJ...531..438B}.
This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius\footnote{We adopt the equatorial radius of Jupiter, {\rjup} = 7.15$\times$10$^9$~cm.} R = 1~{\rjup}.
There is an $H$ = 12.3 reference star (2MASS~J08354383$-$0819212) at a separation of 28$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).

2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L} and Li absorption \citep{2008ApJ...686..528L}.
This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}  \citep{2010ApJ...723..684B}, suggesting a near equator-on orientation.  \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
There are three suitably bright reference stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}. We chose 2MASS~J18212622+1414064 (visible in Figure~\ref{fig:images}) with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.

To characterize the atmospheric regions probed by our observations, we analyzed previously 
obtained IRTF/SpeX data for these sources \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} indicates near-infrared
classifications of L7 for {\sha} and L5 for {\shb} (Figure~\ref{fig:tbright}). The former is considerably later than the L5 optical classification previously reported by \citet{2003AJ....126.2421C}. We confirm the intermediate low surface gravity classification (INT-G) reported by \citet{2016ApJ...833...96L} based on the indices of \citet{2013ApJ...772...79A} using an L7 classification. The discrepancy between the optical and near-infrared classifications of this source is likely related to surface gravity effects. {\shb}, on the other hand, is a good match to the L5 spectral standard and has a field dwarf gravity classification.

We computed brightness temperature spectra from these data as
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1},
\end{equation}
where the surface flux density $F_{\lambda,surf}$ is computed as
\begin{equation}
F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2.
\end{equation}
$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ is the source distance and $R$ is the source radius.
We have ignored limb darkening in our calculations, which affects the surface intensity of brown dwarf surfaces \citep[e.g.][]{2011A&A...529A..75C}.
Since there are few empirical constraints on limb darkening for L-dwarfs, we assume a uniform brightness temperature surface, which gives an average brightness temperature of a non-homogeneous surface.

Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes. We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming bolometric luminosities from \citet{2015ApJ...810..158F} for {\sha} and from\footnote{The parameters reported for {\shb} in \citet{2016ApJS..225...10F} are in error, but have been updated here based on a forthcoming erratum (J.\ Faherty, 2017, priv.\ comm.).} \citet{2016ApJS..225...10F} for {\shb} (Table~\ref{tab:bdProp}). Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\lbol} and radii were propagated by Monte Carlo simulation.  For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
For {\shb}, we assumed a lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}. The \citet{2003A&A...402..701B} evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.

@@

Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.  The spectral peaks for {\sha} are around 1800--1850~K in the field surface gravity case, and decline from 1700~K at $J$-band (1.2~$\micron$) to 1580~K at $K$-band (2.2~$\micron$) in the low surface gravity case.
We compared these two cases to solar-metallicity BT-Settl spectral models from \citet{2012RSPTA.370.2765A}, with {\teff} and {\logg} parameters consistent with the bolometric luminosity of {\sha} and the adopted ages (again based on the \citealt{2003A&A...402..701B} evolutionary models).
To achieve temperatures and gravities between the pre-computed spectra in the BT-Settl atmospheric grid, we interpolated the spectra.
Both models overlap the data to some degree, although the young model shows an increasing brightness temperature with wavelength rather than a decreasing temperature.  These comparisons slightly favor the field surface gravity case, although differences in the properties of dust between source and models likely play a significant role. For {\shb}, 
brightness temperatures range from 1850~K at $J$-band to 1670~K at $K$-band, again overlapping but declining more strongly with wavelength than the equivalent spectral model, which has a {\teff} similar to that inferred by \citet{2016ApJS..225...10F} and the  \citet{2015ApJ...810..158F} {\teff}/spectral type relation.

\section{Observations}\label{sec:obs}
\begin{deluxetable*}{lcccccccc}[b]
\tablecaption{Observations\label{tab:obsParam}}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{2}{c}{Observation Epoch (UT)} \\
 \cline{2-3}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM \@ $H$} \\
 & &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 272 & 45 & 4.65 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 352 & 60 & 7.47 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including array sampling and overheads. The FWHM is the measured full width at half maximum of the spatial point spread function around H band (1.7$\mu$m), taken as the median value over the entire time series.}
\end{deluxetable*}

We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. 
Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis. This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differential color refraction. The effective resolution of the spectral data, set by seeing and pointing errors, was $\lambda$/$\Delta\lambda$ $\approx$ 50. Integration times were 45~s and 60~s for {\sha} and {\shb}, respectively. The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
